### 2012-06-21 inst/examples/criticaltransition.Rmd
add warning signals stats calc to criticaltransitions

`ro cache=FALSE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE or`

@@

>>>>

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="criticaltransition/" or`

@@

## Calculate warning signals

``` {r libs2}
library(earlywarning)
````

``` {r earlywarning}
acor_tau <- dt[fishstock > 1.5, 
               warningtrend(data.frame(time=time, value=fishstock),
                            window_autocorr),
               by=reps]

var_tau <- dt[fishstock > 1.5, 
              warningtrend(data.frame(time=time, value=fishstock),
                          window_var),
              by=reps]
````

``` {r modelbased}
m <- dt[fishstock > 1.5, 
        stability_model(data.frame(time=time, value=fishstock),
                          "LSN")$pars["m"],
        by=reps]
````

``` {r summaryplot}
signals <- melt(data.frame(var=var_tau$V1, acor=acor_tau$V1, m=m$V1))
ggplot(signals) + geom_density(aes(value)) + facet_wrap(~variable)
````
